Fitting the Undetected: Light-curve Feature Estimation in the Presence of Non-detections

### 2013-03-26 tex/ms.tex
tiny typo in parameter list
author list, acks, moved figures

\shorttitle{Fitting the Undetected}
\shortauthors{}
\title{Fitting the Undetected:  Light-curve Feature Estimation in the Presence of Non-detections}
\author{
Some wild \& crazy guys
}
%
%\altaffiltext{1}{Astronomy Department, University of California, Berkeley, CA, 94720-7450, USA}
%\altaffiltext{2}{Statistics Department, University of California, Berkeley, CA, 94720-7450, USA}
%\altaffiltext{*}{E-mail: {\tt jwrichar@stat.berkeley.edu}}

% Note the status (in preparation, MNRAS submitted date, ApJ accepted date, in press etc).
\slugcomment{in preparation}

@@

\subsection{The Full Model}
\label{sec:full}
Putting it all together, we can write down the likelihood of the data, $D_i$, for the parameters $\theta$, on a single epoch, as
\begin{eqnarray}\displaystyle
\label{eqn:lik}
p(D_i|\theta,I) &=& \int_0^{\infty} p(\fobs |\sigma^2_i,\theta,I)\, p(\sobs | \fobs, \sigma^2_i,\theta,I)\, p(\sigma^2_i | \theta, I)\,\dd \sigma^2_i
\\
\label{eqn:likpar}
\theta &\equiv& (\omega, A_0, \{A_k, B_k\}_{k=1}^K, \eta^2\,\mu_i^2, B, V_B, V_{\sigma}, S, V_S) \quad ,
\end{eqnarray}
where we have inserted the expressions from Equations (\ref{eq:mlik}), (\ref{eq:slik}), and (\ref{eq:sigma_prior}), and integrated over the nuisance parameter $\sigma^2_i$.

@@

\begin{figure}[hbtp]
  \begin{center}
    \includegraphics[width=\textwidth,%
      trim=3cm 12cm 5cm 3cm, clip=true]{gm/gm.pdf}
  \end{center}
  \caption{The graphical representation of the probability distribution.
    \label{fig:graph}}
\end{figure}

@@

\begin{figure*}
\begin{center}
\includegraphics[angle=0,width=6.5in]{../plots/mira_simulated.pdf}
\end{center}
\caption{ Folded light curves for data simulated from the Mira variable ASAS 235627-4947.2 using the prescription in \S\ref{ss:mirasim}.  Blue tick marks along the bottom axis denote phases where there were non-detections.  As the original flux measurements are dimmed by higher factors, the troughs of the sinusoidal light curve are censored, resulting in an incomplete view of the data.  \label{fig:mirasim}}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics[angle=0,width=6.5in]{../plots/mira_periods_LS_vs_Censored.pdf}
\end{center}
\caption{ .  \label{fig:miraP}}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics[angle=0,width=6.5in]{../plots/mira_period_amplitude_relation.pdf}
\end{center}
\caption{ .  \label{fig:miraPA}}
\end{figure*}

@@

\acknowledgements

@@

>>>>

\shorttitle{Fitting the Undetected}
\shortauthors{Richards, Hogg, Long, Foreman-Mackey}
\title{Fitting the Undetected:  Light-curve Feature Estimation in the Presence of Non-detections}
\author{
Joseph W. Richards\altaffilmark{1, 2, 3, *},
David W. Hogg\altaffilmark{4, 5},
James P. Long\altaffilmark{2},
Daniel Foreman-Mackey\altaffilmark{4}
}
%
\altaffiltext{1}{Astronomy Department, University of California, Berkeley, CA, 94720-7450, USA}
\altaffiltext{2}{Statistics Department, University of California, Berkeley, CA, 94720-7450, USA}
\altaffiltext{3}{wise.io, 2150 Shattuck Ave., suite 525, Berkeley, CA, 94704, USA}
\altaffiltext{4}{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY 10003, USA}
\altaffiltext{5}{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\altaffiltext{*}{\texttt{jwrichar@stat.berkeley.edu}}

% Note the status (in preparation, MNRAS submitted date, ApJ accepted date, in press etc).
\slugcomment{DRAFT 2013-03-26 / in preparation}

@@

\subsection{The Full Model}
\label{sec:full}
Putting it all together, we can write down the likelihood of the data, $D_i$, for the parameters $\theta$, on a single epoch, as
\begin{eqnarray}\displaystyle
\label{eqn:lik}
p(D_i|\theta,I) &=& \int_0^{\infty} p(\fobs |\sigma^2_i,\theta,I)\, p(\sobs | \fobs, \sigma^2_i,\theta,I)\, p(\sigma^2_i | \theta, I)\,\dd \sigma^2_i
\\
\label{eqn:likpar}
\theta &\equiv& (\omega, A_0, \{A_k, B_k\}_{k=1}^K, \eta^2, B, V_B, V_{\sigma}, S, V_S) \quad ,
\end{eqnarray}
where we have inserted the expressions from Equations (\ref{eq:mlik}), (\ref{eq:slik}), and (\ref{eq:sigma_prior}), and integrated over the nuisance parameter $\sigma^2_i$.

@@

@@

@@

@@

@@

\acknowledgements It is a pleasure to thank Josh Bloom (Berkeley) for
valuable discussions and comments.  Partial support for this project
was provided by [JWR: PUT GRANT NUMBERS HERE], NASA grant NNX12AI50G,
and NSF grant IIS-1124794.

@@

\clearpage
\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth,%
      trim=3cm 12cm 5cm 3cm, clip=true]{gm/gm.pdf}
  \end{center}
  \caption{The graphical representation of the probability distribution.
    \label{fig:graph}}
\end{figure}

\clearpage
\begin{figure}
\begin{center}
\includegraphics[angle=0,width=6.5in]{../plots/mira_simulated.pdf}
\end{center}
\caption{ Folded light curves for data simulated from the Mira variable ASAS 235627-4947.2 using the prescription in \S\ref{ss:mirasim}.  Blue tick marks along the bottom axis denote phases where there were non-detections.  As the original flux measurements are dimmed by higher factors, the troughs of the sinusoidal light curve are censored, resulting in an incomplete view of the data.  \label{fig:mirasim}}
\end{figure}

\clearpage
\begin{figure}
\begin{center}
\includegraphics[angle=0,width=6.5in]{../plots/mira_periods_LS_vs_Censored.pdf}
\end{center}
\caption{ .  \label{fig:miraP}}
\end{figure}

\clearpage
\begin{figure}
\begin{center}
\includegraphics[angle=0,width=6.5in]{../plots/mira_period_amplitude_relation.pdf}
\end{center}
\caption{ .  \label{fig:miraPA}}
\end{figure}
